Micromechanism of Cold Deformation of Two Phase Polycrystalline Ti-Al Alloy with void

### 2018-11-23 draft/alexpub.tex
小改毕

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{Cold deformation behavior of poly crystalline metallic material is affected by intrinsic defects such as dislocation, void, inclusion etc.  Existing studies on $\alpha_2(\rm{Ti_3Al})$+$\gamma(\rm{TiAl})$  two phase Ti-Al alloy cover about deformation behavior mainly on macro scale. This paper focuses on the cold deformation mechanism of two phase Ti-Al alloy at micro scale, and  the role of void  in deformation process. Molecular dynamics simulations were performed to study the evolution of micro structure of material under uniaxial tension. Interaction between spherical nano void with different size and position was also examined in the simulation. The results show that (1) $\gamma$ phase is the major deformation source of the two phase alloy; (2) void detracts the strength of the two phase alloy, while the position of void affect the degree of this subtraction, voids located at the boundary of $\alpha_2$/$\gamma$ phase have significant detraction to strength.}
% Keywords
\keyword{two phase Ti-Al alloy, void, molecular dynamics, cold deformation}

@@

The interaction of particle in the material is determined by interatomic potential. Many reported simulation cases of deform and crack propagation in metal materials were performed with embedded atomic method due to its better accuracy in metal lattice compare with F-S and L/J \cite{Ko2015,Zepeda-Ruiz2017,Fan2018a}. Embedded atom method (MEAM) potential developed by Zope and Mishin \cite{Zope2003} was used in the study. The simulation is submitted by MD simulations with the Large-scale Atomic/Molecular Massively Parallel Simulator (LAMMPS) open-source code \cite{Plimpton1995}. We performed constant-pressure and constant-temperature (NPT) molecular dynamics simulation at room temperature (298K). The definition of potential is as following:

@@

Two phase Ti-Al alloy is composed of $\gamma $-TiAl and $\alpha_2$-$\rm Ti_3Al$ has a fcc type cell with an $L1_0$ structure, and $\alpha_2$-$\rm Ti_3Al$ has a hcp structure, these two types of initial cells are shown in Fig. \ref{fig:tial-cell}, constructing parameters of the two type of unit cell are given by table \ref{tab:lattice_parameter}. Periodic boundary conditions (PBC) are applied along three directions, which makes polycrystal with periodic nanovoid structures. The initial dimension of simulation cell is $L_x =200$ \si{\angstrom}, $L_y = $180\si{\angstrom}, $L_z = 210$ \si{\angstrom}, and each model contains about 460,000 atoms. The grain orientation and size were randomly created with Voronoi method by code ATOMSK \cite{Hirel2015}, and resulting in the arbitrary shape and orientation of the grains. Uniaxial load was applied to the model at a strain rate of $5\times10^8\ \rm{s}^{-1}$. 
% In order to study the deformation mechanism of the two phase alloy and the effect of void, three types of models were created: Type-1.model without any void; Type-2. models with different size void inside $\alpha_2$ phase; Type-3. models with void at $\alpha_2-\gamma$ interface. \ref{tab:lattice_parameter}. The simulation cells of two phase polycrystalline with an initially spherical void at different position are shown in figure .
\subsection{Analysis method}
In order to identify typical defects in the deformed model, a hybrid analysis method was used with free code ovito\cite{Stukowski2010a}.Dislocation is visualized by DXA method, and Centro-symmetry parameter(CSP) is used to tell grain boundary from  $\alpha_2$ phase and $\gamma$ phase. The definition of CSP is as following:

@@

%	/home/alex/Documents/violet/draft/img/perfect-line.pdf
Deformation process of the model without void is shown in Fig. \ref{fig:deformation-pf}. The strength of the model without void is 5.3 GPa. According to stress response under constant rate of strain rate, the whole tensile process can be divided into four stages: 
stage - \uppercase\expandafter{\romannumeral1}: elastic stage, from $\epsilon = 0$ to $\epsilon = 0.092$, including key point 1,
stage - \uppercase\expandafter{\romannumeral2}: yield stage, ranging from $\epsilon = 0.092$ to $\epsilon = 0.101$, including key points 2 to 6,
stage - \uppercase\expandafter{\romannumeral3}: cracking stage, ranging from $\epsilon = 0.101$ to $\epsilon = 0.112$, including key point 7 to 10,
stage - \uppercase\expandafter{\romannumeral4}: fracture stage. Following discussion concentrates on deformation phenomena that rely on the elastro-plastic codeformation of the $\gamma$ and $\alpha_2$ phases and on the particular point defect situation occurring in two phase alloys.

@@

% Due to this effect ( $\alpha_2$ + $\gamma$ ) alloys exhibit some remarkable properties that are unlike those of either constituent.
\subsection{Deformation Mechanism of Two Phase TiAl Alloy without voids}
Snapshots of atom configuration at the 3 of 10 key points are shown by Fig. \ref{fig:Defect}.  Atoms with ordered configuration  of $\gamma$ phase grains have been removed in Fig. \ref{fig:Defect}(a) and (b),\ $\alpha_2$ phase and defects inside grains have been left. Similarly, $\gamma$ phase grain have been removed in Fig. \ref{fig:Defect}(c) and (d), the defects of $\alpha_2$ phase have been left.  The results show that, at stage \uppercase\expandafter{\romannumeral1}, the structure of material is under typical elastic deformation, the size of simulation box enlarged due to the loading. In this stage, deformation of the two phase are compatible. Emission of dislocation and evolution of defects initiated at the end of stage \uppercase\expandafter{\romannumeral1}. A  great number of dislocation emitted inside $\gamma$ phase at earlier part of stage \uppercase\expandafter{\romannumeral2}, however, the dislocation inside $\alpha_2$ phase was emitted at the end of stage \uppercase\expandafter{\romannumeral2} is shown by Fig. \ref{fig:Defect}(c).  
\begin{figure}[ht] 
	\centering
	\includegraphics[width=1\linewidth]{img/def-box}
	\caption{Microstructure evolution inside $\gamma$ phase(a,b), $\alpha_2$ phase(c,d) during yield stage}
	\label{fig:Defect}
\end{figure}
Experiments have shown that the velocity of dislocation motion is sensitive to stress and temperature\cite{Stein1960}. The brittleness of two phase Ti-Al alloy attributed to the poor mobility of dislocation at room temperature. Velocity of a screw dislocation can be estimated by Escaig's elastic model \cite{Escaig1968}, it can be written as:
\begin{equation}\label{eq:temp-dis}
v = v_0\ e^{-\Delta H(\tau^*)/kT}
\end{equation}
where the prefactor $v_0$ gives the velocity that would be obtained for each potential mobility, $L$ represents the free length of screw character of dislocation, $\Delta H(\tau^*)$ is activation enthalpy determined by loading conditions. The effect of temperature on the mobility can be evaluated under different loading conditions, thus we chose  $\tau_1^*>\tau_2^*>\tau_3^*$ in formulation (\ref{eq:temp-dis}), normalized velocity of dislocation motion is shown by Fig. \ref{fig:temp}. The  velocity  of dislocation movement rise along with increase of  stress, the mobility  of dislocation is relatively poor at 298 K. Due to motion of dislocations is inactive inside $\alpha_2$ phase,  typical strengthening mechanism closely related with interaction between grain boundary and dislocation can not be dramatic at room temperature, piling up of dislocations is not observed in this simulation, which is shown in Fig. \ref{fig:Defect}.
\begin{figure}[ht]
	\centering
	\begin{minipage}{0.495\textwidth}
		\includegraphics[width=1\linewidth]{img/temp}
		\centering
		\caption{Normalized velocity of dislocation motion under different loading conditions}
		\label{fig:temp}
	\end{minipage}	
	\hfill
	\begin{minipage}{0.495\textwidth}		
		\includegraphics[width=1\linewidth]{img/dis-summary}
		\centering
		\caption{Dislocation length under differentstrain }
		\label{fig:disum}
	\end{minipage}
\end{figure}

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width=1\linewidth]{img/slice-view}
	\caption{ Model with no void (b), with void inside $\alpha_2$ phase (c) with void at $\alpha_2-\gamma$ interface (d)}
	\label{fig:model-creation}
\end{figure}

@@

\begin{figure}[ht]
	\centering
	\begin{minipage}{0.495\textwidth}
		\includegraphics[width=1\linewidth]{img/allline}
		\centering
		\caption{Stress-strain response of models}
		\label{fig:stress&strain}
	\end{minipage}	
	\hfill
	\begin{minipage}{0.495\textwidth}		
		\includegraphics[width=1\linewidth]{img/effect_of_vol}
		\centering
		\caption{Yield strength of material with void}
		\label{fig:strength}
	\end{minipage}
\end{figure}

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width=1\linewidth]{"img/orowan"}
	\caption{Orowan process in $\alpha_2$-phase (atoms with regular arrangement have been removed)}
	\label{fig:orowan}
\end{figure}
Void inside $\alpha_2$ phase induced considerable misfit-stress fields and thus can influence material properties pronouncedly. Such stress fields surrounding the second-phase particles can be due to misfit between $\alpha_2$ phase atoms and surface atoms surounding the void. That's a possibly favorable effect of second-phase particles that void contribution to the enhancement of mechanical strength. The strengthening effect of the particle inside single phase TiAl alloy has been verified by experiment \cite{Zghal1998}. Considering yielding of a material as related to glide of dislocations, any mechanism obstructing dislocation glide improves the mechanical strength. The defect evolution neighboring the void during yield stage is shown in Fig. \ref{fig:orowan}(a), the role of void is similar to second-phase particles. It servers as obstacles for dislocation migration which is shown by Fig. \ref{fig:orowan}(b): the stress fields surrounding the second-phase particles block migrating dislocation, the void particle acts as pinning point. The dislocation can pass two pinning points under shear  stress , and the critic value depends on the distance between  obstacles, it is be given by \cite{Xiong2015}:
\begin{equation} \label{eq:orowan} 
\tau_0 = Gb/d
\end{equation}
where $d$ represents the distance between two obstacles A and B in Fig. \ref{fig:orowan} , reflects the dependence of the critical shear stress $\tau_0$ on the second-phase particle density and distribution. This mechanism for hardening is designated as the Orowan process with $\tau_0$ as the Orowan shear stress. As a result of the Orowan process, upon passage of the pinning points by a series of gliding dislocations, a system of concentric loops is formed around the second-phase particles. Consequently, the effective average distance between the second phase particles has decreased to $d$ which implies a necessary increase of the value of critical shear stress required for continuation of dislocation glide. The width of a burgers vector, will be generated at both sides of a crystal along the direction of  burgers vector after dislocation traversing the entire crystal, as is shown in the third subfigure of Fig. \ref{fig:orowan}(b).

\begin{figure}[ht]
	\centering
	\includegraphics[width=1\linewidth]{"img/void-gb"}
	\caption{(a) Fracture mode of two types of model  (b)Evolution of void at  phase boundary}
	\label{fig:void-gb}
\end{figure}
Effect of voids at different positions on the crack mode of the material are shown by Fig. \ref{fig:void-gb}(a). The model with void fractured cross the grain, and the model with void at $\alpha_2 / \gamma$ boundary resulted a large crack along the boundary under tensile loading. The difference of crack mode can attribute to the position of void and the evolution of the defect. Nucleation, emission of Shockley partial dislocation affect the evolution of the void at boundary greatly due to the anisotropy of two phases on the both sides of the phase boundary. The void weaken the strength of the grain it locates,  $\alpha_2$ phase grain is easy to deformed under shear stress, thus that caused the crack initiated inside grain and finally caused fracture across the grain. Deformation mechanism of the model with void at boundary can be  more complex due to the interaction between void and phase boundary. In elastic stage, the system composed of $\alpha_2$ phase, $\gamma$ phase and void is in equilibrium, internal stress are balanced under compatible deformation as is shown by the first subfigure of Fig. \ref{fig:void-gb}(b). In the middle moment of yield stage, partial dislocation with Burgers vector $1/6[\overline{2}\ \overline{1}\ 1]$ emitted from surface of void in Fig. \ref{fig:void-gb}(b)-2. The micro crack initialed from the zone neighbor  the interface between void and boundary, that quickly caused abrupt decohension of phase boundary. That accounts for the reason that material with void at $\alpha_2 / \gamma$ phase boundary is weaker than other cases. 
\section{conclusion}
In this paper, deformation behavior of two phase Ti-Al alloy under tensile loading was simulated with MD method. The mechanism of deformation was investigated under atomic scale, and the effect of void on the properties of two phase Ti-Al alloy was also studied.  The conclusions are as follows:\\
(1) Major deformation component of the two phase TiAl alloy is $\gamma$ phase,$\alpha_2$ phase is harder to be deformed, this inhomogeneity results in cracks at interface of the two phase. \\
(2) Effect of  void on the strength of the two phase alloy is sensitive to the location of  void. Void inside grain hasss detraction to the strength of material because the engthening mechanism similar to second phase particle. Void at $\alpha_2 / \gamma$ boundary is most risky situation for two phase alloy because of fast fracture along boundary.

>>>>

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{Cold deformation behavior of poly crystalline metallic material is affected by intrinsic defects such as dislocation, void, inclusion etc.  Existing studies on $\alpha_2(\rm{Ti_3Al})$+$\gamma(\rm{TiAl})$  two phase Ti-Al alloy cover about deformation behavior mainly on macro scale. This paper focuses on the cold deformation mechanism of two phase Ti-Al alloy at micro scale, and  the role of void  in deformation process. Molecular dynamics simulations were performed to study the evolution of micro structure of material under uniaxial tension. Interaction between spherical nano void with different size and position was also examined in the simulation. The results show that (1) $\gamma$ phase is the major deformation source of the two phase alloy. (2) void detracts the strength of the two phase alloy, while the position of void affect the degree of this subtraction, voids located at the boundary of $\alpha_2$/$\gamma$ phase have significant detraction to strength.}
% Keywords
\keyword{two phase Ti-Al alloy; void; molecular dynamics; cold deformation}

@@

The interaction of particles in the material is determined by interatomic potential. Many reported simulation cases of deform and crack propagation in metal materials were performed with embedded atomic method due to its better accuracy in metal lattice compare with F-S and L/J \cite{Ko2015,Zepeda-Ruiz2017,Fan2018a}. Embedded atom method (MEAM) potential developed by Zope and Mishin \cite{Zope2003} was used in the study. The simulation is performed  with the Large-scale Atomic/Molecular Massively Parallel Simulator (LAMMPS) open-source code \cite{Plimpton1995}. We performed constant-pressure and constant-temperature (NPT) MD simulation at room temperature (298K). Definition of the potential is as following:

@@

Two phase Ti-Al alloy is composed of $\gamma $-TiAl and $\alpha_2$-$\rm Ti_3Al$ has a fcc type cell with an $L1_0$ structure, and $\alpha_2$-$\rm Ti_3Al$ has a hcp structure, these two types of initial cells are shown in Fig. \ref{fig:tial-cell}, constructing parameters of the two type of unit cell are given by table \ref{tab:lattice_parameter}. Periodic boundary conditions (PBC) are applied along three directions, which makes polycrystal with periodic nanovoid structures. The initial dimension of simulation cell is $L_x =200$ \si{\angstrom}, $L_y = $180\si{\angstrom}, $L_z = 210$ \si{\angstrom}, and each model contains about 460,000 atoms. The model contains 6 grains, with random shape and orientation were created with Voronoi method. Uniaxial load was applied to the model at a strain rate of $5\times10^8\ \rm{s}^{-1}$. 
% In order to study the deformation mechanism of the two phase alloy and the effect of void, three types of models were created: Type-1.model without any void; Type-2. models with different size void inside $\alpha_2$ phase; Type-3. models with void at $\alpha_2-\gamma$ interface. \ref{tab:lattice_parameter}. The simulation cells of two phase polycrystalline with an initially spherical void at different position are shown in figure .
\subsection{Analysis method}
In order to identify typical defects in the deformed model, a hybrid analysis method was used with free code ovito\cite{Stukowski2010a}.Dislocation is visualized by DXA method, and centro-symmetry parameter(CSP) is used to deffer grain boundaries from  $\alpha_2$ phase and $\gamma$ phase. The definition of CSP is as following:

@@

%	/home/alex/Documents/violet/draft/img/perfect-line.pdf
Deformation process of the model without void is shown in Fig. \ref{fig:deformation-pf}. The strength of the model without void is 5.3 GPa. According to stress response under constant rate of strain rate, the whole tensile process can be divided into four stages: 
stage - \uppercase\expandafter{\romannumeral1}: elastic stage, from $\epsilon = 0$ to $\epsilon = 0.092$, including key point 1,
stage - \uppercase\expandafter{\romannumeral2}: yield stage, ranging from $\epsilon = 0.092$ to $\epsilon = 0.101$, including key points 2 to 6,
stage - \uppercase\expandafter{\romannumeral3}: cracking stage, ranging from $\epsilon = 0.101$ to $\epsilon = 0.112$, including key point 7 to 10,
stage - \uppercase\expandafter{\romannumeral4}: fracture stage. Following discussion concentrates on deformation phenomena that rely on the elastro-plastic codeformation of the $\gamma$ and $\alpha_2$ phases and on the particular point defect situation occurred in two phase alloys.

@@

% Due to this effect ( $\alpha_2$ + $\gamma$ ) alloys exhibit some remarkable properties that are unlike those of either constituent.
\subsection{Deformation Mechanism of Two Phase TiAl Alloy without voids}
Snapshots of atom configuration at the 3 of 10 key points are shown by Fig. \ref{fig:Defect}.  Atoms with ordered configuration  of $\gamma$ phase grains have been removed in Fig. \ref{fig:Defect}(a) and (b),\ $\alpha_2$ phase and defects inside grains have been left. Similarly, $\gamma$ phase grain have been removed in Fig. \ref{fig:Defect}(c) and (d), the defects of $\alpha_2$ phase have been left.  The results show that, at stage \uppercase\expandafter{\romannumeral1}, the structure of material is under typical elastic deformation, the size of simulation box enlarged due to the loading. In this stage, deformation of the two phase are compatible. Emission of dislocation and evolution of defects initiated at the end of stage \uppercase\expandafter{\romannumeral1}. A  great number of dislocation emitted inside $\gamma$ phase at earlier part of stage \uppercase\expandafter{\romannumeral2}, however, the dislocation inside $\alpha_2$ phase was emitted at the end of stage \uppercase\expandafter{\romannumeral2} is shown by Fig. \ref{fig:Defect}(c).  
\begin{figure}[ht] 
	\centering
	\includegraphics[width=1\linewidth]{img/def-box}
	\caption{Microstructure evolution inside $\gamma$ phase(a,b), $\alpha_2$ phase(c,d) during yield stage}
	\label{fig:Defect}
\end{figure}
Experiments have shown that the velocity of dislocation motion is sensitive to stress and temperature\cite{Stein1960}. The brittleness of two phase Ti-Al alloy attributed to the poor mobility of dislocation at room temperature. Velocity of a screw dislocation can be estimated by Escaig's elastic model \cite{Escaig1968}, it can be written as:
\begin{equation}\label{eq:temp-dis}
v = v_0\ e^{-\Delta H(\tau^*)/kT}
\end{equation}
where the prefactor $v_0$ gives the velocity that would be obtained for each potential mobility, $L$ represents the free length of screw character of dislocation, $\Delta H(\tau^*)$ is activation enthalpy determined by loading conditions. The effect of temperature on the mobility can be evaluated under different loading conditions, thus we chose  $\tau_1^*>\tau_2^*>\tau_3^*$ in formulation (\ref{eq:temp-dis}), normalized velocity of dislocation motion is shown by Fig. \ref{fig:temp}. The  velocity  of dislocation movement rise along with increase of  stress, the mobility  of dislocation is relatively poor at 298 K. Due to motion of dislocations is inactive inside $\alpha_2$ phase,  typical strengthening mechanism closely related with interaction between grain boundary and dislocation can not be dramatic at room temperature, piling up of dislocations is not observed in this simulation, which is shown in Fig. \ref{fig:Defect}.
\begin{figure}[ht]
	\centering
	\begin{minipage}{0.495\textwidth}
		\includegraphics[width=1\linewidth]{img/temp}
		\centering
		\caption{Normalized velocity of dislocation motion under different loading conditions}
		\label{fig:temp}
	\end{minipage}	
	\hfill
	\begin{minipage}{0.495\textwidth}		
		\includegraphics[width=1\linewidth]{img/dis-summary}
		\centering
		\caption{Summary of didderent types of dislocation under different strain }
		\label{fig:disum}
	\end{minipage}
\end{figure}

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width=1\linewidth]{img/slice-view}
	\caption{Model of the simulation(a) and sliced view of the model with no void(b), with void inside $\alpha_2$ phase(c) with void at $\alpha_2 / \gamma$ interface(d)}
	\label{fig:model-creation}
\end{figure}

@@

\begin{figure}[ht]
	\centering
	\begin{minipage}{0.495\textwidth}
		\includegraphics[width=1\linewidth]{img/allline}
		\centering
		\caption{Stress-strain response of the materials under tensile loading}
		\label{fig:stress&strain}
	\end{minipage}	
	\hfill
	\begin{minipage}{0.495\textwidth}		
		\includegraphics[width=1\linewidth]{img/effect_of_vol}
		\centering
		\caption{Yield strength of the materials with different size void}
		\label{fig:strength}
	\end{minipage}
\end{figure}

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width=1\linewidth]{"img/orowan"}
	\caption{Orowan process occurred inside $\alpha_2$ phase grain (removed atoms with regular arrangement)}
	\label{fig:orowan}
\end{figure}
Void inside $\alpha_2$ phase induced considerable misfit-stress fields and thus can influence material properties pronouncedly. Such stress fields surrounding the second-phase particles can be due to misfit between $\alpha_2$ phase atoms and surface atoms surounding the void. That's a possibly favorable effect of second-phase particles that void contribution to the enhancement of mechanical strength. The strengthening effect of the particle inside single phase TiAl alloy has been verified by experiment \cite{Zghal1998}. Considering yielding of a material as related to glide of dislocations, any mechanism obstructing dislocation glide improves the mechanical strength. The defect evolution neighboring the void during yield stage is shown in Fig. \ref{fig:orowan}(a), the role of void is similar to second-phase particles. It servers as obstacles for dislocation migration which is shown by Fig. \ref{fig:orowan}(b): the stress fields surrounding the second-phase particles block migrating dislocation, the void particle acts as pinning point. The dislocation can pass two pinning points under shear  stress , and the critic value depends on the distance between  obstacles, it is be given by \cite{Xiong2015}:
\begin{equation} \label{eq:orowan} 
\tau_0 = Gb/d
\end{equation}
where $d$ represents the distance between two obstacles A and B in Fig. \ref{fig:orowan} , reflects the dependence of the critical shear stress $\tau_0$ on the second-phase particle density and distribution. This mechanism for hardening is designated as the Orowan process with $\tau_0$ as the Orowan shear stress. As a result of the Orowan process, upon passage of the pinning points by a series of gliding dislocations, a system of concentric loops is formed around the second-phase particles. Consequently, the effective average distance between the second phase particles has decreased to $d$ which implies a necessary increase of the value of critical shear stress required for continuation of dislocation glide. The width of a burgers vector, will be generated at both sides of a crystal along the direction of  burgers vector after dislocation traversing the entire crystal, as is shown in the third subfigure of Fig. \ref{fig:orowan}(b).

\begin{figure}[ht]
	\centering
	\includegraphics[width=1\linewidth]{"img/void-gb"}
	\caption{(a) Fracture mode of two types of model  (b)Evolution of void at $\alpha_2 / \gamma$ phase boundary}
	\label{fig:void-gb}
\end{figure}
Effect of voids at different positions on the crack mode of the material are shown by Fig. \ref{fig:void-gb}(a). The model with void fractured cross the grain, and the model with void at $\alpha_2 / \gamma$ boundary resulted a large crack along the boundary under tensile loading. The difference of crack mode can attribute to the position of void and the evolution of the defect. Nucleation, emission of Shockley partial dislocation affect the evolution of the void at boundary greatly due to the anisotropy of two phases on the both sides of the phase boundary. The void weaken the strength of the grain it locates,  $\alpha_2$ phase grain is easy to deformed under shear stress, thus that caused the crack initiated inside grain and finally caused fracture across the grain. Deformation mechanism of the model with void at boundary can be  more complex due to the interaction between void and phase boundary. In elastic stage, the system composed of $\alpha_2$ phase, $\gamma$ phase and void is in equilibrium, internal stress are balanced under compatible deformation as is shown by the first subfigure of Fig. \ref{fig:void-gb}(b). In the middle moment of yield stage, partial dislocation with Burgers vector $1/6[\overline{2}\ \overline{1}\ 1]$ emitted from surface of void in Fig. \ref{fig:void-gb}(b)-2. The micro crack initialed from the zone neighbor  the interface between void and boundary, that quickly caused abrupt decohension of phase boundary. That accounts for the reason that material with void at $\alpha_2 / \gamma$ phase boundary is weaker than other cases. 
\section{conclusion}
In this paper, deformation behavior of two phase Ti-Al alloy under tensile loading was simulated with MD method. The mechanism of deformation was investigated under atomic scale, and the effect of void on the properties of two phase Ti-Al alloy was also studied.  The conclusions are as follows:\\
(1) Major deformation component of the two phase TiAl alloy is $\gamma$ phase,$\alpha_2$ phase is harder to be deformed, this inhomogeneity results in cracks at interface of the two phase. \\
(2) Effect of  void on the strength of the two phase alloy is sensitive to the location of  void. Void inside grain hasss detraction to the strength of material because the engthening mechanism similar to second phase particle. Void at $\alpha_2 / \gamma$ boundary is most risky situation for two phase alloy because of fast fracture along boundary.
